Real-Time Adaptive Ultrasound Algorithms \vspace{0.5cm}

### 2013-12-06 ThesisJP/Introduction/introduction.tex
ThesisJP: Added reference list.

\section{Motivation and aims of study}
\label{sec:motivationAndAims}

\section{Thesis outline}

@@

\subsubsection{Paper no. 1:\\
An Optimised GPU Implementation of the MVDR Beamformer for Active Sonar Imaging}

@@

\subsubsection{Paper no. 2:\\
Implementing Capon Beamforming on a GPU for Real-Time Cardiac Ultrasound Imaging}

@@

\subsubsection{Paper no. 3:\\
Capon Beamforming Applied on Moving Objects - An Analysis of Local Lateral Shift-Invariance}

@@

\subsubsection{Paper no. 4:\\
Adaptive Volume Rendering of Cardiac 3D Ultrasound Images - Utilizing Blood Pool Statistics}

@@

\subsubsection{Paper no. 5:\\
Huygens on Speed: Interactive Simulation of Ultrasound Pressure Fields}

@@

\subsubsection{Papers included in the thesis}
\begin{enumerate}
	\item J. I. Buskenes, J. P. \AA{}sen, C.-I. C. Nilsen and A. Austeng, "An Optimised GPU Implementation of the MVDR Beamformer for Active Sonar Imaging", {\it Submitted for review to IEEE Transactions on Oceanic Engineering}.
	\item 
\end{enumerate}

\subsubsection{Conference proceedings}
\begin{enumerate}
	\item 
	\item 
\end{enumerate}

\subsubsection{Presentations and abstracts}
\begin{enumerate}
	\item
\end{enumerate}

>>>>

\section{Background and motivation}

\section{Aims of study}

@@

\subsubsection{Paper no. 1 (Chapter 3):\\
An Optimised GPU Implementation of the MVDR Beamformer for Active Sonar Imaging}

@@

\subsubsection{Paper no. 2 (Chapter 4):\\
Implementing Capon Beamforming on a GPU for Real-Time Cardiac Ultrasound Imaging}

@@

\subsubsection{Paper no. 3 (Chapter 5):\\
Capon Beamforming Applied on Moving Objects - An Analysis of Local Lateral Shift-Invariance}

@@

\subsubsection{Paper no. 4 (Chapter 6):\\
Adaptive Volume Rendering of Cardiac 3D Ultrasound Images - Utilizing Blood Pool Statistics}

@@

\subsubsection{Paper no. 5 (Chapter 7):\\
Huygens on Speed: Interactive Simulation of Ultrasound Pressure Fields}

@@

\subsubsection{Papers included in the thesis}
\begin{enumerate}
	\item J. I. Buskenes, \textbf{J. P. \AA{}sen}, C.-I. C. Nilsen and A. Austeng, "An optimised GPU implementation of the MVDR beamformer for active sonar imaging", {\it Submitted for review to IEEE Transactions on Oceanic Engineering}.
	\item \textbf{J. P. \AA{}sen}, J. I. Buskenes, C.-I. C. Nilsen, A. Austeng and S. Holm, "Implementing Capon beamforming on a GPU for real-time cardiac ultrasound imaging", {\it IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control, vol. XY, January 2014}.
 	\item \textbf{J. P. \AA{}sen}, A. Austeng and S. Holm, "Capon beamforming applied on moving objects - An analysis of local lateral shift-invariance", {\it Submitted for review to IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control}.
	\item \textbf{J. P. \AA{}sen}, E. Steen, G. Kiss, A. Thorstensen and S. I. Rabben, "Adaptive volume rendering of cardiac 3D ultrasound images - utilizing blood pool statistics", {\it Proc. SPIE Medical Imaging 2012}.
	\item \textbf{J. P. \AA{}sen} and S. Holm, "Huygens on speed: Interactive simulation of ultrasound pressure fields", {\it Proc. IEEE Ultrasonics Symposium 2012}.
\end{enumerate}

\subsubsection{Related publications not included in the thesis}
\begin{enumerate}
	\item \textbf{J. P. \AA{}sen}, J. I. Buskenes, C.-I. C. Nilsen, A. Austeng and S. Holm, "Implementing Capon Beamforming on the GPU for Real-Time Cardiac Ultrasound Imaging", {\it Proc. IEEE Ultrasonics Symposium 2012}.

	\item J. I. Buskenes, \textbf{J. P. \AA{}sen}, C.-I. C. Nilsen and A. Austeng, "Adapting the Minimum variance beamformer to a graphics processing unit for active sonar imaging systems", {\it Proc. Meetings on Acoustics 2013}.

	\item G. Kiss, E. Steen, \textbf{J. P \AA{}sen} and H. Torp, "GPU volume rendering in 3D echocardiography: real-time pre-processing and ray-casting", {\it Proc. IEEE Ultrasonics Symposium 2010}.

	\item G. Kiss, \textbf{J. P. \AA{}sen}, J. Bogaert, B. H. Amundsen, P. Claus, J. R. M. D'hooge and H. Torp, "Multi-modal cardiac image fusion and visualization on the GPU", {\it Proc. IEEE Ultrasonics Symposium 2011}.

	\item E. S. Br\o{}nstad, \textbf{J. P. \AA{}sen}, H. Torp and G. Kiss, "Visibility driven visualization of 3D cardiac ultrasound data on the GPU", {\it Proc. IEEE Ultrasonics Symposium 2012}.
\end{enumerate}
